### 2017-06-01 R/oregon.Rmd
Cleaned up edits from vargo a little bit
Removed RI bit from Oregon demo

We'll store the vector of means in a variable called _meanVec_ and then view that vector.
```{r misc322, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
meanVec <- getMeans(ITHIM.baseline)
meanVec
```

@@

### Road Injuries
#### Road Injuries File Format

If road injury data is present it can be included in the same manner.

```{r misc123, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
roadInjuriesFile <- "~/ITHIM/inst/roadInjuries.csv"
```

```{r misc220, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.baseline <- createITHIM(activeTransportFile = activeTransportFile,
                              GBDFile = GBDFile,
                              roadInjuriesFile = roadInjuriesFile)
```

@@

### Session Info & Package Test
```{r sessionInfo, eval = FALSE, echo = TRUE, results = "show", warning = FALSE, error = FALSE, message = FALSE}
library("testthat")
test_package("ITHIM")
sessionInfo()
```

>>>>

We'll store the vector of means in a variable called _meanVec_ and then view that vector.

```{r misc322, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
meanVec <- getMeans(ITHIM.baseline)
meanVec
```

@@

#### Road Injuries File Format

@@

### Session Info & Package Test
```{r sessionInfo, eval = TRUE, echo = TRUE, results = "show", warning = FALSE, error = FALSE, message = FALSE}
library("testthat")
test_package("ITHIM")
sessionInfo()
```
